Title

### 2024-05-06 paper/main.tex
updates

\section{Introduction}
Para 1: Many Causal discovery algorithms but commonly constructed manually.

To perform any causal effect identification or estimation in Directed Acyclic
Graph(DAG) based causal inference usually requires to come up with the DAG
structure. Learning these DAG structures from data is known as \emph{causal
discovery}. Plenty of algorithms have been developed for these in the
literature such as constraint-based methods such as PC, FCI, score based
methods such as Hill-Climb Search, GES, and constrained continuous optimization
based such as No TEARS.

Para 2: Reasons behind this

@@

Para 3: Importance of testing

@@

Para 4: Mixed data testing

One of the limitations here is there are no effect size measures available for

Para 5: Contributions

\section{Background}
\subsection{Continuous Variables}
\subsection{Discrete Variables}
\subsection{Ordinal Variables}
\subsection{Ordinal and Continuous Variables}

>>>>

\section{Introduction}
\textbf{Para 1: Many Causal discovery algorithms but commonly constructed manually.}

To perform any causal effect identification or estimation in Pearl's Directed
Acyclic Graphs (DAGs) based causal inference usually requires to come up with
the DAG structure. Learning these DAG structures from data is known as
\emph{causal discovery}. Plenty of algorithms have been developed for these in
the literature such as constraint-based methods such as PC, FCI, score based
methods such as Hill-Climb Search, GES, and constrained continuous optimization
based such as No TEARS.

\textbf{Para 2: Reasons behind this}

@@

\textbf{Para 3: Importance of testing, include modification indices}

@@

\textbf{Para 4: Mixed data testing}

One of the limitations here is there are no effect size measures available for mixed data.

\textbf{Para 5: Contributions}
\begin{enumerate}
	\item An effect size measure for mixed data. 
	\item A web-based tool to help with both model testing and construction. Combining both domain knowledge and data.
\end{enumerate}

\section{Background}
\todo[inline]{Add notation used here}

\subsection{Continuous Variables}
Correlation coefficient and partial correlation coefficient.

\subsection{Discrete Variables}
Chi-Squared and Cram\'er's V

\subsection{Ordinal and Continuous Variables}
Polyserial Correlation

\subsection{Ordinal Variables}
Polychoric Correlation

\subsection{Mixed data}
Background on CI tests for mixed data; but no effect size measure.
